Unit tests

### 2018-04-05 SupportingInformation.Rmd
working on BB7 warning message, I think I fixed it

<!--Do the main analysis-->
```{r RES_plankton_north_sea, echo=F, cache=T, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

>>>>

<!--Do the main analysis-->
```{r RES_plankton_north_sea, echo=F, cache=T, results="hide", cache.extra=list(seed,data_plankton_north_sea,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

### 2018-04-05 Tests.Rmd
working on BB7 warning message, I think I fixed it

Now apply the function:
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(d,mtime("OurBiCopSelect.R"))}
families<-c(1,3,4,5,13)
BivMS_res_test<-OurBiCopSelect(d[,1],d[,2],families=families,gofnormal=F,status=TRUE)
```

>>>>

Now apply the function:
```{r bivmodselect_test, echo=F, cache=T, cache.extra=list(d,mtime("OurBiCopSelect.R"))}
families<-c(1,3,4,5,13)
BivMS_res_test<-OurBiCopSelect(d[,1],d[,2],families=families,gofnormal=T,status=TRUE)
```
